\HeaderA{OptimDesControl}{Set parameters controlling numerical methods for OptimDes and np.OptimDes}{OptimDesControl}
\keyword{design}{OptimDesControl}
\keyword{optimize}{OptimDesControl}
\begin{Description}\relax
Set parameters controlling numerical methods for \code{\LinkA{OptimDes}{OptimDes}} and \code{\LinkA{np.OptimDes}{np.OptimDes}}
\end{Description}
\begin{Usage}
\begin{verbatim}
OptimDesControl(trace=FALSE,tol=0.01,conv=1e-6,rho.int=c(0,1),aboveMin=1.05)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{trace}] A logical value indicating if a
trace of the iteration
progress should be printed.  Default is \code{FALSE}.  If
\code{TRUE} the sample size \code{n}, the corresponding optimal
correlation \code{rho} and minimized \code{EDA}(\code{ETSL}) are
printed at the conclusion of each iteration.
\item[\code{tol}] \code{tol} is the
desired accuracy for \code{optimize}. Default is 0.01.
\item[\code{conv}] The desired convergence accuracy for \code{C1} and
\code{C2}. Default is 1e-6.
\item[\code{rho.int}] A vector containing
the end-points of the interval to
be searched for the optimal \code{rho}. Default is (0, 1).
\item[\code{aboveMin}] The minimization method searches by increasing order
from the single-stage
sample size until the criteria exceeds the current minimum by a 
multiplicative factor of \code{aboveMin}.  The search will also 
terminate if \code{sum(m.init)} is reached.
\end{ldescription}
\end{Arguments}
\begin{Author}\relax
Bo Huang \email{<huang@stat.wisc.edu>} and Neal Thomas
\end{Author}
\begin{References}\relax
Case M. D. and Morgan T. M. (2003) Design of Phase II cancer trials
evaluating survival probabilities. \emph{BMC Medical Research
Methodology}, \bold{3}, 7.

Lin D. Y., Shen L., Ying Z. and Breslow N. E. (1996) Group seqential
designs for monitoring survival probabilities. \emph{Biometrics},
\bold{52}, 1033--1042.

Simon R. (1989) Optimal two-stage designs for phase II clinical
trials. \emph{Controlled Clinical Trials}, \bold{10}, 1--10.
\end{References}
\begin{SeeAlso}\relax
\code{\LinkA{OptimDes}{OptimDes}}, \code{\LinkA{np.OptimDes}{np.OptimDes}}
\end{SeeAlso}

