\HeaderA{weibPmatch}{Compute the shape or scale parameter for a Weibull
distribution so it has a specified event rate at a specified time.}{weibPmatch}
\keyword{hplot}{weibPmatch}
\begin{Description}\relax
Determine the shape or scale parameter of a Weibull distribution so
it has event rate P0 at time x.  If the shape is specified, the scale
parameter is computed, and if the scale is specified, the shape
parameter is computed.
\end{Description}
\begin{Usage}
\begin{verbatim}
weibPmatch(x, p0, shape, scale)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{x}] Time for targetted event rate 
\item[\code{p0}] Event rate at time x (1- survival rate). 
\item[\code{shape}] If specified, the necessary scale parameter is computed 
\item[\code{scale}] If specified, the necessary shape parameter is computed  
\end{ldescription}
\end{Arguments}
\begin{Details}\relax
The time and event rate must be supplied.  Either the shape or
scale parameter must also be specified, but not both.  The R
parameterization of the Weibull distribution is used.
\end{Details}
\begin{Value}
A single numerical value is returned, either the shape or scale
parameter, depending on which is specified by the user.
\end{Value}
\begin{Author}\relax
Bo Huang \email{<huang@stat.wisc.edu>} and Neal Thomas
\end{Author}
\begin{References}\relax
Johnson, N. L., Kotz, S. and Balakrishnan, N. (1995) Continuous
Univariate Distributions, volume 1, chapter 21. Wiley, New York.
\end{References}
\begin{SeeAlso}\relax
\code{\LinkA{weibull.plot}{weibull.plot}},\code{\LinkA{pweibull}{pweibull}}, \code{\LinkA{OptimDes}{OptimDes}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}

library(OptimPhase2)
param <- c(1, 1.09, 2, 1.40)
x<-1

p0<-pweibull(x,param[1],param[2])
p1<-pweibull(x,param[3],param[4])

weibull.plot(param,x)

### equivalent to simple call
paramNew<-c(param[1], weibPmatch(x,p0,param[1]), param[3], weibPmatch(x,p1,param[3]))
weibull.plot(paramNew, x)

### null curve with different shape
paramNew<-c(3.0, weibPmatch(x,p0,3.0), param[3], weibPmatch(x,p1,param[3]))
weibull.plot(paramNew, x)

### alternative curve with different scale
paramNew<-c(param[1], param[2], weibPmatch(x,p1,scale=2), 2)
weibull.plot(paramNew, x)

\end{ExampleCode}
\end{Examples}

