\HeaderA{weibull.plot}{Plot Weibull Survival Curves}{weibull.plot}
\keyword{hplot}{weibull.plot}
\begin{Description}\relax
Plot Weibull survival curves with differences at a target time highlighted. Designed for use with the \code{param}
values input to function \code{\LinkA{OptimDes}{OptimDes}}.
\end{Description}
\begin{Usage}
\begin{verbatim}
weibull.plot(param, x, l.type = 1:3, l.col = c("blue", "red"), ...)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{param}] A four-element vector containing: the shape parameter of the Weibull distribution under the
null hypothesis, the scale parameter of the Weibull distribution under the
null hypothesis, the shape parameter of the Weibull distribution under the
alternative hypothesis, the scale parameter of the Weibull distribution under the
alternative hypothesis.
\item[\code{x}] Survival time of interest (e.g., 1 year).
\item[\code{l.type}] Line types for the plot. Default is \code{1-3}.
\item[\code{l.col}] Line colors for the plot. Default is \code{"blue"} for
the null survival curve, \code{"red"} for the alternative survival curve.
\item[\code{...}] Further graphical arguments, see \code{plot.default}.
\end{ldescription}
\end{Arguments}
\begin{Author}\relax
Bo Huang \email{<huang@stat.wisc.edu>} and Neal Thomas
\end{Author}
\begin{References}\relax
Johnson, N. L., Kotz, S. and Balakrishnan, N. (1995) Continuous
Univariate Distributions, volume 1, chapter 21. Wiley, New York.
\end{References}
\begin{SeeAlso}\relax
\code{\LinkA{dweibull}{dweibull}}, \code{\LinkA{OptimDes}{OptimDes}},
\code{\LinkA{weibPmatch}{weibPmatch}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}
param <- c(1, 1.09, 2, 1.40)
x <- 1

weibull.plot(param,x)

\end{ExampleCode}
\end{Examples}

